# Quality {#quality .tabset .tabset-fade .tabset-pills}

A record is considered _completed_ when it has at least the sheets 
**anagrafica**, **accettazione**, **pim**, **dimissione** marked as completed.

---



## Complete records {.tabset .tabset-dropdown}

```{r}
qualityReportUI("q_overall")
```

```{r, context = "server"}
qualityReport("q_overall", data = full_records)
```




## Hospitalized {.tabset .tabset-dropdown}

Records are considered related to an "hospitalized" patient if the field 
**reparto** is not missing in the sheet **dimissione**.

```{r}
qualityReportUI("q_hosp")
```

```{r, context = "server"}
data_hosp <- filter(full_records, !is.na(reparto))
qualityReport("q_hosp", data = data_hosp)
```




## Data errors {.tabset .tabset-dropdown}

Two types of errors are considerend at the moment:

1. missing data
2. outlier values out of reasonable range, i.e., which have a distance from the
   median that is farther than 1.5 times the inter quartile range.


### Missing values

```{r}
errorReportUI("q_error")
```

```{r, context = "server"}
errorReport("q_error")
```





### Possible errors into the data



