# Descriptive and Demographic {#descriptives .tabset .tabset-fade .tabset-pills}


In Italy there are 23 medical surgical (M/S) Pediatric Intensive Care Units (PICUs):

- 11 in the north
- 8 in the center
- 4 in the south

of the country.

Data reported here analyze patients admitted in PICUs from
`r params$first_y` to `r params$last_y`.

Only children 0 -- 16 years old who have a severity score on admission
which allow to estimate a Standardized Mortality Ratio (SMR) were
considered.

### Overview

Below are reported all the admissions in the registry. Exclusion
criteria were" preterm or > 16 years old, or not completed data entry

---

###### Info: Click on a tab to explore its content {- .alert .alert-info}

## PICUs {.tabset .tabset-dropdown}

```{r}
fluidPage(
  ymdInputUI("birthday", "When were you born?"),
  textOutput("age")
)
```

```{r, context = "server"}
birthday <- ymdInput("birthday")
  
  age <- reactive({
    req(birthday())
    (birthday() %--% today()) %/% years(1)
  })
  
  output$age <- renderText({
    paste0("You are ", age(), " years old")
  })
```
### Partecipating Units

foo

### Number of beds

foo

## Admissions {.tabset .tabset-dropdown}

foo

### Trends

foo

### Distributions

foo

### Gender

foo

### Ethnicity

foo

### Age

foo




## Demographics {.tabset .tabset-dropdown}

foo
