--- 
params:
    cache: TRUE
    export: FALSE
    first_y: 1992
    last_y:  2020
    auto_update: TRUE
    force_update: FALSE
    max_days_update: 28
    
    quality_completed: "Completed"
    quality_type: "Proportion"

output:
    bookdown::html_document2:
        toc: true
        toc_float: true
        toc_depth: 2
        df_print: paged

runtime: shiny_prerendered

title: "TIPNet report (`r paste0(params$first_y, ' - ', params$last_y)`)"

author: "Italian Pediatric Intensive Care Units Network (**TIPNet**)
  </br>
  \\ \\ \\ \\ in collaboration with:
  </br>
  \\* Italian Society of Pediatric and Neonatal Anesthesia and Intensive Care (**SARNePI**)
  </br>
  \\* Unit of Biostatistics, Epidemiology and Public Health (**UBEP**) --- University of Padova."

biblio-style: apalike
link-citations: yes
bibliography:
  - bibliography.bib
  - packages.bib

---


```{r setup, include=FALSE}
# This is run only once both to the render and server side, and it
# is the very first chunk of code that will be run

options(
  knitr.duplicate.label = 'allow',
  width = 144
)

knitr::opts_chunk$set(
  comment = "",
  cache = FALSE,
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  
  width      = 150,   # output size
  out.width = "100%", # part of output covered
  fig.width = 11,     # set size creation-time
  dpi = 192           # set output resolution (impact weight)
 )

if (
  !is.null(getOption("TIPNet_dev")) && isTRUE(getOption("TIPNet_dev"))
) {
    all_attached <- paste0("package:", names(sessionInfo()$otherPkgs))
    attempt::attempt(suppressWarnings(invisible(lapply(
      all_attached, detach, character.only = TRUE, unload = TRUE
    ))), silent = TRUE)
    rstudioapi::documentSaveAll()
    roxygen2::roxygenise(package.dir = here::here(".."))
    devtools::load_all(quiet =  TRUE)
} else {
  library(tipnet.ubesp)
}

library(tidyverse)
library(lubridate)
library(plotly)
library(shiny)
library(DT)
library(glue) 
library(here)

last_file <- file.path(data_path(), "tipnet.rds")
set.seed(1)
```


```{r data, include=FALSE, cache=params$cache, cache.extra=tools::md5sum(last_file)}
# This run only once bot in the render and server side

# cache.extra option in the knitr tags here above needs to speed up
# normal computation and running time (render side) as the data are not
# changed. Note that server-side data are loaded from the render-side
# if included in the chunk named "data" (like this is), hence setting
# cache.extra provide a further speed up.

is_to_update <- params$auto_update &&
  is_expired(last_file, params$max_days_update)

if (params$force_update || is_to_update) db_update_from_server()

tipnet <- readr::read_rds(last_file) 
tipnet_meta <- file.path(data_path(), "tipnet_meta.rds") %>% 
  readr::read_rds()

global_vars_list <- tipnet.ubesp:::generate_main_data()
purrr::iwalk(global_vars_list,~ assign(.y, .x, pos = 1))
```


<!-- ```{r server-start, include = FALSE} -->
<!-- # this run only once on the server session when it starts (after -->
<!-- # setup and data chunks) -->
<!-- ``` -->

**Last report update**: `r as.Date(file.info('index.Rmd')$mtime)`  ---  **Last data update**: `r as.Date(file.info(last_file)$mtime)`

# Colophon {-}

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

**Network coordinator**: Andrea Wolfler, MD ([Department of Anesthesia and Intensive Care Unit](https://www.asst-fbf-sacco.it/reparti-e-servizi/info/anestesia-e-rianimazione-pediatrica) -- [Children’s Hospital Vittore Buzzi](https://www.asst-fbf-sacco.it/reparti-e-servizi/ricerca-reparto-presidio/buzzi)) --- Milan

**In collaboration with**: Unit of Biostatistics, Epidemiology and Public Helath ([UBEP](https://ubesp.jimdo.com/)), [Department of Cardiac, Toracic, Vascular sciences and Public Health](https://www.dctv.unipd.it/) -- [University of Padova](https://www.unipd.it/) --- Interuniversity Consortium

- Dario Gregori (head of UBEP)
- Corrado Lanera (Laboratory of Artificial Intelligence for Medical Sciences)
- Giulia Lorenzoni, Honoria Ocagli (Laboratory of Clinical Epidemiology)
- Rosanna Comoretto (Laboratory for Health Service Research)
- Matteo Martinato, Laura Nasato (Service for Clinical Trials and Biometrics)

**Business intelligence analyst**: Roberta Amato

**IT Project Managers**: Dario Gregori, Corrado Lanera

**With the contribution of**:

- F. Racca, J Gualino - Alessandria
- F. Ferrero, R Osello, R Gilodi - Novara
- I Salvo, E. Zoia, A. Mandelli - Milano
- E Calderini, C. Montani, E. Prandi - Milano
- P. Biban, P Santuz - Verona
- A. Pettenazzo, A Amigoni - Padova
- S. Furlan, F Savron - Trieste
- F Caramelli, C. Mondardini, E. Iannella - Bologna
- C Cecchetti, D Perrotta - Roma
- S Picardo, E Rossetti - Roma
- M Corbari - Roma
- G. Conti, M Piastra, O. Genovese - Roma
- R Testa, A Dolcini, L. D’Amato - Napoli
- G Coffaro, A. M. Guddo, A. M. Giglio - Palermo
- E Gitto - Messina
- G Stancanelli - Catania

**TIPNet study group** - participating center:

- Department of Anesthesia and Intensive Care, Children’s Hospital Sant’Antonio e Biagio e Cesare Arrigo, Alessandria:
- Department of Pediatrics, Ospedale Maggiore della Carità, Novara:
- Department of Anesthesia and Intensive Care, Children’s Hospital V Buzzi, Milan:
- Department of Anesthesia and Intensive Care, Fondazione IRCCS Ca Granda, Ospedale Maggiore Policlinico, Milan:
- Department of Pediatric Anesthesia and Intensive Care, Spedali Civili, Brescia
- Department of Neonatal and Paediatric Intensive Care, Azienda Ospedaliera Universitaria Integrata, Verona
- Department of Woman’s and Child’s Health, Pediatric ICU, University Hospital, Padova
- Department of Anesthesia and Intensive Care, Institute for Maternal and Child health, IRCCS Burlo Garofolo, Trieste
- Department of Pediatric Anesthesia and Intensive Care, Ospedale Sant’Orsola Malpighi, Bologna
- Department of Anesthesia and Intensive Care, Children’s Hospital Meyer, Firenze
- Department of Anesthesia and Intensive Care, Children’s Hospital Bambino Gesù, Rome DEA, ARCO, Palidoro
- Anesthesia and Intensive Care Department, Pediatric ICU, Policlinico Universitario A.Gemelli, Università Cattolica del Sacro Cuore, Rome
- Department of Anesthesia and Intensive Care, Children’s Hospital Santobono-Pausillipon, Napoli
- Department of Anesthesia and Intensive Care, Children’s Hospital G Di Cristina, Palermo
- Department of Anesthesia and Intensive Care Ospedale Garibaldi – Nesima, Catania
- Department of Pediatrics Ospedale Policlinico –Universitario G Martino, Messina

</div>








```{r, child = "005-quality.Rmd"}
```

<!-- ```{r, child = "010-descriptives.Rmd"} -->
<!-- ``` -->

<!-- ```{r, child = "020-origin.Rmd"} -->
<!-- ``` -->

<!-- ```{r, child = "030-ccc.Rmd"} -->
<!-- ``` -->

<!-- ```{r, child = "040-severity.Rmd"} -->
<!-- ``` -->

<!-- ```{r, child = "050-los.Rmd"} -->
<!-- ``` -->








```{r, results='asis', eval=!params$export}
cat("# Download current report {-}")
```


```{r, eval=!params$export}
shiny::downloadLink("report", "Generate report")
```

```{r, context="server", eval=!params$export}

output$report <- downloadHandler("tipnet-repor.html",
  
  content = function(file) {
    to_copy <- list.files(".", all.files = TRUE, include.dirs = TRUE) %>% 
      setdiff(c(".", "..", "static"))
    
    dir <- fs::dir_create("./static")
    
    file.copy(to_copy, dir,
        overwrite = TRUE,
        recursive = TRUE,
        copy.date = TRUE # this is needed to not invalidate caches
    )
    report <- file.path(dir, "index.Rmd")
    
    out <- readr::read_lines(report) %>% 
      stringr::str_replace("^runtime: shiny_prerendered$", "") %>% 
      stringr::str_replace_all(
        "\\.tabset \\.tabset-fade \\.tabset-pills",
        ""
      ) 
    readr::write_lines(out, report)
    
    # Set up parameters to pass to Rmd document
    params <- list(
      export = TRUE,
      quality_completed = input[[NS("q_overall", "completed")]],
      quality_type = input[[NS("q_overall", "type")]]
      # foo = input$foo, # bring the current state of the report
    )

    # Knit the document, passing in the `params` list, and eval it in a
    # child of the global environment (this isolates the code in the
    # document from the code in this app).
    withr::with_options(
      list(TIPNet_dev = FALSE),
      
      rmarkdown::render(report, output_file = file,
        params = params,
        envir = new.env(parent = globalenv())
      )
    )
  }
)
```








# References {-}

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
