---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# tipnet.ubesp

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/UBESP-DCTV/tipnet.ubesp?branch=master&svg=true)](https://ci.appveyor.com/project/UBESP-DCTV/tipnet.ubesp)
[![Travis build status](https://travis-ci.org/UBESP-DCTV/tipnet.ubesp.svg?branch=master)](https://travis-ci.org/UBESP-DCTV/tipnet.ubesp)
[![Codecov test coverage](https://codecov.io/gh/UBESP-DCTV/tipnet.ubesp/branch/master/graph/badge.svg)](https://codecov.io/gh/UBESP-DCTV/tipnet.ubesp?branch=master)
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
<!-- badges: end -->

The goal of tipnet.ubesp is to implement and collect all the code needed
for the development of the TIPNet reports by UBESP.

## Installation

You can install the development version from
[GitHub](https://github.com/) with the following procedure:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("UBESP-DCTV/tipnet.ubesp")
```

## Code of Conduct
Please note that the 'tipnet.ubesp' project is released with a
[Contributor Code of Conduct](.github/CODE_OF_CONDUCT.md). By
contributing to this project, you agree to abide by its terms.
