# Descriptive and Demographic {#descriptives .tabset .tabset-fade .tabset-pills}


In Italy there are 23 medical surgical (M/S) Pediatric Intensive Care Units (PICUs):

- 11 in the north
- 8 in the center
- 4 in the south

of the country.

The number of units participating in the registry increased from 13 in
2011 to 18 in 2014.

Due to different reasons, not all the units recorded efficiently during
the years. This is the first report published by the network. Data
reported here analyze patients admitted in PICUs during
`r params$period`.

Only children 0 -- 16 years old who have a severity score on admission
which allow to estimate a Standardized Mortality Ratio (SMR) were
considered.

### Overview

Below are reported all the admissions in the registry. Exclusion
criteria were" preterm or > 16 years old, or not completed data entry
```{r}
DT::datatable(intro_accettazione,
    filter = "top",
    selection = "multiple",
    rownames = FALSE
)

included <- accettazione %>% 
    mutate(`Date of admission` = lubridate::dmy(ingresso_dt)) %>% 
    filter(
        `Date of admission` >= lubridate::dmy("01/01/2010"),
        `Date of admission` <= lubridate::dmy("31/12/2014")
    ) %>% 
    mutate(
        Center = as.factor(center),
        Ingresso = `Date of admission`,
        Preterm = d_is_prematuro | d_ex_prematuro,
        `Over 16`   = eta > 16 * 365.25
    ) %>% 
    filter(!Preterm, !`Over 16`)
```


- record in the registry are `r nrow(intro_accettazione)`
- record analyzed are `r nrow(included)`



---

###### Info: Click on a tab to explore its content {- .alert .alert-info}

## PICUs {.tabset .tabset-dropdown}


### Partecipating Units

##### Warn: Data missing {- .alert .alert-warning}


### Shiny-engine examples:

#### pre_pim k-means clustering live"

```{r, eval=!params$export}
sidebarLayout(
    sidebarPanel(
    
        selectInput('xcol', 'X Variable', names(pre_pim),
            selected = params$pre_pim_x
        ),
    
        selectInput('ycol', 'Y Variable', names(pre_pim),
            selected = params$pre_pim_y
        ),
    
        numericInput('clusters', 'Cluster count', min = 1, max = 9,
            value = params$pre_pim_nclust
        )
    
    ),
    mainPanel(
        plotOutput('plot1')
    )
)
```

```{r, context="server", eval=!params$export}
# Combine the selected variables into a new data frame
  selectedData <- reactive({
    pre_pim[, c(input$xcol, input$ycol)] %>% 
      remove_missing()
  })

  clusters <- reactive({
    kmeans(selectedData(), input$clusters)
  })

  output$plot1 <- renderPlot({
    palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
      "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999"))

    par(mar = c(5.1, 4.1, 0, 1))
    plot(selectedData(),
         col = clusters()$cluster,
         pch = 20, cex = 3)
    points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
  })
```

```{r, eval=params$export}
selected_data <- pre_pim[, c(params$pre_pim_x, params$pre_pim_y)] %>% 
      remove_missing()
clusters <- kmeans(selected_data, params$pre_pim_nclust)

par(mar = c(5.1, 4.1, 0, 1))
plot(selected_data, col = clusters$cluster, pch = 20, cex = 3)
points(clusters$centers, pch = 4, cex = 4, lwd = 4)
```


### Number of beds
```{r, echo=FALSE, eval=!params$export}
sliderInput("bins", "Number of bins:",
    min = 1, max = 50, value = params$bins
)
plotOutput("distPlot2")
```


```{r, context="server", eval=!params$export}
output$distPlot2 <- renderPlot({
  gg_bins(input$bins)
})

```

```{r, eval=params$export}
glue("Number of bins: {params$bins}")
gg_bins(params$bins)
```


## Admissions {.tabset .tabset-dropdown}

### Trends
```{r}
ggplotly(gg_admission_trends)
```


### Distributions

foo

### Gender

foo

### Ethnicity

foo

### Age

foo

## Demographics {.tabset .tabset-dropdown}
```{r, eval=!params$export}
selectInput(
  'breaks', label = 'Number of bins:',
  choices = c(10, 20, 35, 50), selected = params$breaks
)
plotOutput("distPlot3")
```


```{r, context="server", eval=!params$export}
output$distPlot3 <- renderPlot({
  gg_breaks(input$breaks)
})
```

```{r, eval=params$export}
glue("Number of breaks: {params$breaks}")
gg_breaks(params$breaks)
```
