--- 
params:
    export: FALSE
    period: "2010 -- 2014"
    picu_type: ["M/S", "C/N", "n/p"]
    breaks: 20
    bins: 30
    iris_x: !r names(iris)[[1]]
    iris_y: !r names(iris)[[2]]
    iris_nclust: 3
    pre_pim_x: "be"
    pre_pim_y: "pim2"
    pre_pim_nclust: 3

output:
    bookdown::html_document2:
        toc: true
        toc_float: true
        toc_depth: 2
        df_print: paged

runtime: shiny_prerendered

title: "`r paste0('TIPNet long-term report, years ', params$period)`"
subtitle: '<style> div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;} </style><div class = "blue"> Prototype by Corrado Lanera and Dario Gregori<br>**Artificial Intelligence and Data Mining Lab** within the<br>**Unit of Biostatistics, Epidemiology, and Public Health** of the<br>_Department of Cardiac, Thoracic, Vascular Sciences and Public Health_ at the University of Padova</div>'
author: "Italian Pediatric Intensive Care Units Network (TIPNet) in collaboration with Italian Society of Pediatric and Neonatal Anesthesia and Intensive Care (SARNePI) and CINECA"
date: "**Last update**: `r Sys.Date()`"

biblio-style: apalike
link-citations: yes
bibliography:
  - bibliography.bib
  - packages.bib

description: "`r paste0('Prototype example for the TIPNet long-term report (years ', params$period, ')')`"
---


```{r setup, include=FALSE}
options(knitr.duplicate.label = 'allow')

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)

suppressPackageStartupMessages(library(tidyverse, quietly = TRUE))
suppressPackageStartupMessages(library(plotly, quietly = TRUE))
suppressPackageStartupMessages(library(DT, quietly = TRUE))
suppressPackageStartupMessages(library(glue, quietly = TRUE))
suppressPackageStartupMessages(library(here, quietly = TRUE))
# suppressPackageStartupMessages(library(tipnet.ubesp, quietly = TRUE))

# When approved, those function should be included in the `tipnet.ubesp`
# package.
gg_picu_type <- function(param) {
  filter(foo, type %in% param) %>% 
    mutate(year = as.numeric(year)) %>% 
    ggplot(aes(x = year, y = beds, colour = unit)) +
    geom_point() +
    geom_smooth(se = TRUE) +
    xlab("Years") +
    ylab("Beds")
}

gg_bins <- function(param) {
    x <- faithful[, 2]  # Old Faithful Geyser data
    bins <- seq(min(x), max(x), length.out = param + 1)
    hist(x, breaks = bins, col = 'darkgray', border = 'white')
}


gg_breaks <- function(param) {
  par(mar = c(4, 4, .1, .5))
  hist(
    faithful$eruptions, as.numeric(param),
    col = 'gray', border = 'white',
    xlab = 'Duration (minutes)', main = ''
  )
}
```

```{r data, include=FALSE, cache=TRUE, cache.extra=file.info(here("..", "..", "..", "data"))$mtime}
# cache.extra option in the knitr tags here above needs to speed up
# normal computation and running time (render side) as the data are not
# changed. Note that server-side data are loaded from the render-side
# if included in the chunck named "data" (like this is), hence setting
# cache.extra provide a further speed up.


# DATA IMPORT =========================================================
anagrafica <- read_rds(here("..", "..", "..", "data", "tip_anagrafica.rds"))

accettazione <- read_rds(
  here("..", "..", "..", "data", "tip_accettazione.rds")
)

pre_pim <- read_rds(
  here("..", "..", "..", "data", "pre_pim.rds")
) %>% # this is only for the sample kmeans model plot
  select_if(is.double)

# INTRO ===============================================================
intro_accettazione <- accettazione %>% 
    mutate(`Date of admission` = lubridate::dmy(ingresso_dt)) %>% 
    filter(
        `Date of admission` >= lubridate::dmy("01/01/2010"),
        `Date of admission` <= lubridate::dmy("31/12/2014")
    ) %>% 
    select(center, `Date of admission`, codpat, d_is_prematuro, d_ex_prematuro, eta) %>% 
    mutate(
        Center = as.factor(center),
        Ingresso = `Date of admission`,
        Preterm = d_is_prematuro | d_ex_prematuro,
        `Over 16`   = eta > 16 * 365.25
    ) %>% 
    distinct() %>% 
    select(Center, `Date of admission`, Preterm, `Over 16`)


# PICUs ===============================================================
# Partecipating Units -------------------------------------------------
# ADMISSIONS ==========================================================
# Trends --------------------------------------------------------------
admission_trends <- intro_accettazione %>%
    mutate(Year = lubridate::year(`Date of admission`)) %>% 
    arrange(Year) %>% 
    group_by(Year) %>% 
    mutate(`Overall admissions` = n()) %>% 
    group_by(Year, Center) %>% 
    mutate(`Center admissions` = n()) %>%
    distinct(
      Center, Year, `Overall admissions`, `Center admissions`
    ) %>% 
    ungroup()

gg_admission_trends <- admission_trends %>% 
        ggplot(aes(x = Year)) +
        geom_line(aes(y = `Overall admissions`)) +
        geom_line(aes(y = `Center admissions`, colour = Center)) +
        ylab("Admissions")

# Distributions -------------------------------------------------------
# Gender --------------------------------------------------------------
# Ethnicity -----------------------------------------------------------
# Age -----------------------------------------------------------------
# 
# DEMOGRAPHICS ========================================================
# 

bar <- read_csv("bar.csv")
n <- 7
units <- letters[seq_len(n)]
foo <- tibble(
    unit = units,
    type = c("M/S", "C/N", "n/p")[sample.int(3, n, replace = TRUE)]
  ) %>% 
  full_join(tibble(
    unit = rep(units, 5),
    year = rep(2010:2014, n),
    beds = sample(c(NA, 0:10), n*5, replace = TRUE)
  ))
```


# Colophon {-}

<style>
div.blue { background-color:#e6f0ff; border-radius: 5px; padding: 20px;}
</style>
<div class = "blue">

**Network coordinator**: Andrea Wolfler, MD ([Department of Anesthesia and Intensive Care Unit](https://www.asst-fbf-sacco.it/reparti-e-servizi/info/anestesia-e-rianimazione-pediatrica) -- [Children’s Hospital Vittore Buzzi](https://www.asst-fbf-sacco.it/reparti-e-servizi/ricerca-reparto-presidio/buzzi)) --- Milan

**In collaboration with**: [Unit of Biostatistics, Epidemiology and Public Helath](https://ubesp.jimdo.com/) ([Department Cardiac, Toracic, Vascular sciences and Public Health](https://www.dctv.unipd.it/) -- [University of Padova](https://www.unipd.it/)) --- Interuniversity Consortium


**Business intelligence analyst**: Roberta Amato

**IT Project Managers**: Chiara Dellacasa, Giulia Stabile

**With the contribution of**:

- F. Racca, J Gualino - Alessandria
- F. Ferrero, R Osello, R Gilodi - Novara
- I Salvo, E. Zoia, A. Mandelli - Milano
- E Calderini, C. Montani, E. Prandi - Milano
- P. Biban, P Santuz - Verona
- A. Pettenazzo, A Amigoni - Padova
- S. Furlan, F Savron - Trieste
- F Caramelli, C. Mondardini, E. Iannella - Bologna
- C Cecchetti, D Perrotta - Roma
- S Picardo, E Rossetti - Roma
- M Corbari - Roma
- G. Conti, M Piastra, O. Genovese - Roma
- R Testa, A Dolcini, L. D’Amato - Napoli
- G Coffaro, A. M. Guddo, A. M. Giglio - Palermo
- E Gitto - Messina
- G Stancanelli - Catania

**TIPNet study group** - participating center:

- Department of Anesthesia and Intensive Care, Children’s Hospital Sant’Antonio e Biagio e Cesare Arrigo, Alessandria:
- Department of Pediatrics, Ospedale Maggiore della Carità, Novara:
- Department of Anesthesia and Intensive Care, Children’s Hospital V Buzzi, Milan:
- Department of Anesthesia and Intensive Care, Fondazione IRCCS Ca Granda, Ospedale Maggiore Policlinico, Milan:
- Department of Pediatric Anesthesia and Intensive Care, Spedali Civili, Brescia
- Department of Neonatal and Paediatric Intensive Care, Azienda Ospedaliera Universitaria Integrata, Verona
- Department of Woman’s and Child’s Health, Pediatric ICU, University Hospital, Padova
- Department of Anesthesia and Intensive Care, Institute for Maternal and Child health, IRCCS Burlo Garofolo, Trieste
- Department of Pediatric Anesthesia and Intensive Care, Ospedale Sant’Orsola Malpighi, Bologna
- Department of Anesthesia and Intensive Care, Children’s Hospital Meyer, Firenze
- Department of Anesthesia and Intensive Care, Children’s Hospital Bambino Gesù, Rome DEA, ARCO, Palidoro
- Anesthesia and Intensive Care Department, Pediatric ICU, Policlinico Universitario A.Gemelli, Università Cattolica
del Sacro Cuore, Rome
- Department of Anesthesia and Intensive Care, Children’s Hospital Santobono-Pausillipon, Napoli
- Department of Anesthesia and Intensive Care, Children’s Hospital G Di Cristina, Palermo
- Department of Anesthesia and Intensive Care Ospedale Garibaldi – Nesima, Catania
- Department of Pediatrics Ospedale Policlinico –Universitario G Martino, Messina

</div>

```{r, child = "010-descriptives.Rmd"}
```

```{r, child = "020-origin.Rmd"}
```

```{r, child = "030-ccc.Rmd"}
```

```{r, child = "040-severity.Rmd"}
```

```{r, child = "050-los.Rmd"}
```



```{r, results='asis', eval=!params$export}
cat("# Download current report {-}")
```


```{r, eval=!params$export}
downloadLink("report", "Generate report")
```

```{r, context="server", eval=!params$export}
output$report <- downloadHandler("tipnet-repor.html",
  
  content = function(file) {
    temp_dir <- tempdir()
    file.copy(".", temp_dir,
        overwrite = TRUE,
        recursive = TRUE,
        copy.date = TRUE # this is needed to not invalidate caches
    )
    temp_report <- file.path(temp_dir, "index.Rmd")
    
    read_lines(temp_report) %>% 
      str_replace("^runtime: shiny_prerendered$", "") %>% 
      str_replace_all(
        "\\.tabset \\.tabset-fade \\.tabset-pills",
        ""
      ) %>% 
      write_lines(temp_report)
    
    # Set up parameters to pass to Rmd document
    params <- list(
      export = TRUE,
      
      breaks = input$breaks,
      bins   = input$bins,
      iris_x = input$xcol,
      iris_y = input$ycol,
      iris_nclust = input$clusters,
      pre_pim_x = input$pre_pim_xcol,
      pre_pim_y = input$pre_pim_ycol,
      pre_pim_nclust = input$pre_pim_clusters
    )

    # Knit the document, passing in the `params` list, and eval it in a
    # child of the global environment (this isolates the code in the
    # document from the code in this app).
    rmarkdown::render(temp_report, output_file = file,
      params = params,
      envir = new.env(parent = globalenv())
    )
  }
)
```


# References {-}

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
