# Descriptive and Demographic {#descriptives .tabset .tabset-fade .tabset-pills}


In Italy there are 23 medical surgical (M/S) Pediatric Intensive Care Units (PICUs):

- 11 in the north
- 8 in the center
- 4 in the south

of the country.

The number of units participating in the registry increased from 13 in
2011 to 18 in 2014.

Due to different reasons, not all the units recorded efficiently during
the years. This is the first report published by the network. Data
reported here analyze patients admitted in PICUs during
`r params$period`.

Only children 0 -- 16 years old who have a severity score on admission
which allow to estimate a Standardized Mortality Ratio (SMR) were
considered.

## PICUs

### Type
```{r, eval=!params$export}
pageWithSidebar(
    
    headerPanel('Iris k-means clustering'),
    
    sidebarPanel(
    
        selectInput('xcol', 'X Variable', names(iris),
            selected = params$iris_x
        ),
    
        selectInput('ycol', 'Y Variable', names(iris),
            selected = params$iris_y
        ),
    
        numericInput('clusters', 'Cluster count', min = 1, max = 9,
            value = params$iris_nclust
        )
    
  ),
  
  mainPanel(
    plotOutput('plot1')
  )
)
```


```{r, context="server", eval=!params$export}
# Combine the selected variables into a new data frame
  selectedData <- reactive({
    iris[, c(input$xcol, input$ycol)]
  })

  clusters <- reactive({
    kmeans(selectedData(), input$clusters)
  })

  output$plot1 <- renderPlot({
    palette(c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3",
      "#FF7F00", "#FFFF33", "#A65628", "#F781BF", "#999999"))

    par(mar = c(5.1, 4.1, 0, 1))
    plot(selectedData(),
         col = clusters()$cluster,
         pch = 20, cex = 3)
    points(clusters()$centers, pch = 4, cex = 4, lwd = 4)
  })
```

```{r, eval=params$export}
selected_data <- iris[, c(params$iris_x, params$iris_y)]
clusters <- kmeans(selected_data, params$iris_nclust)

par(mar = c(5.1, 4.1, 0, 1))
plot(selected_data, col = clusters$cluster, pch = 20, cex = 3)
points(clusters$centers, pch = 4, cex = 4, lwd = 4)
```


### Number of beds
```{r, echo=FALSE, eval=!params$export}
sliderInput("bins", "Number of bins:",
    min = 1, max = 50, value = params$bins
)
plotOutput("distPlot2")
```


```{r, context="server", eval=!params$export}
output$distPlot2 <- renderPlot({
  gg_bins(input$bins)
})

```

```{r, eval=params$export}
glue("Number of bins: {params$bins}")
gg_bins(params$bins)
```


## Admissions

### Trends
```{r}
gg_picu_type(params$picu_type) %>% 
  ggplotly()
```


### Distributions

foo

### Gender

foo

### Ethnicity

foo

### Age

foo

## Demographics
```{r, eval=!params$export}
selectInput(
  'breaks', label = 'Number of bins:',
  choices = c(10, 20, 35, 50), selected = params$breaks
)
plotOutput("distPlot3")
```


```{r, context="server", eval=!params$export}
output$distPlot3 <- renderPlot({
  gg_breaks(input$breaks)
})
```

```{r, eval=params$export}
glue("Number of breaks: {params$breaks}")
gg_breaks(params$breaks)
```
