--- 
output:
  bookdown::html_document2:
    toc: true
    toc_float: true
    df_print: paged
runtime: shiny_prerendered
date: "Last update `r Sys.Date()`"
biblio-style: apalike
link-citations: yes
bibliography:
  - bibliography.bib
  - packages.bib

params:
  period: "2010 - 2014"

title: "`r paste0('TIPNet long-term report, years ', params$period)`"
subtitle: "(prototype by Corrado Lanera^[Unità di Biostatistica, Epidemiologia, e Sanlute Pubblica --- Dip. Scienze Cardio Toraco Vascolari e Salute Pubblica (Univ. di Padova -- IT)])"
author: "Italian Pediatric Intensive Care Units Network (TIPNet) in collaboration with Italian Society of Pediatric and Neonatal Anesthesia and Intensive Care (SARNePI) and CINECA"

description: "`r paste0('Prototype example for the TIPNet long-term report (years ', params$period, ')')`"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE
)
```

# Colophon {-}

**Network coordinator**: Andrea Wolfler, MD ([Department of Anesthesia and Intensive Care Unit](https://www.asst-fbf-sacco.it/reparti-e-servizi/info/anestesia-e-rianimazione-pediatrica) -- [Children’s Hospital Vittore Buzzi](https://www.asst-fbf-sacco.it/reparti-e-servizi/ricerca-reparto-presidio/buzzi)) --- Milan

**In collaboration with**: [Unit of Biostatistics, Epidemiology and Public Helath](https://ubesp.jimdo.com/) ([Department Cardiac, Toracic, Vascular sciences and Public Health](https://www.dctv.unipd.it/) -- [University of Padova](https://www.unipd.it/)) --- Interuniversity Consortium


**Business intelligence analyst**: Roberta Amato

**IT Project Managers**: Chiara Dellacasa, Giulia Stabile

**With the contribution of**:

- F. Racca, J Gualino - Alessandria
- F. Ferrero, R Osello, R Gilodi - Novara
- I Salvo, E. Zoia, A. Mandelli - Milano
- E Calderini, C. Montani, E. Prandi - Milano
- P. Biban, P Santuz - Verona
- A. Pettenazzo, A Amigoni - Padova
- S. Furlan, F Savron - Trieste
- F Caramelli, C. Mondardini, E. Iannella - Bologna
- C Cecchetti, D Perrotta - Roma
- S Picardo, E Rossetti - Roma
- M Corbari - Roma
- G. Conti, M Piastra, O. Genovese - Roma
- R Testa, A Dolcini, L. D’Amato - Napoli
- G Coffaro, A. M. Guddo, A. M. Giglio - Palermo
- E Gitto - Messina
- G Stancanelli - Catania

**TIPNet study group** - participating center:

- Department of Anesthesia and Intensive Care, Children’s Hospital Sant’Antonio e Biagio e Cesare Arrigo, Alessandria:
- Department of Pediatrics, Ospedale Maggiore della Carità, Novara:
- Department of Anesthesia and Intensive Care, Children’s Hospital V Buzzi, Milan:
- Department of Anesthesia and Intensive Care, Fondazione IRCCS Ca Granda, Ospedale Maggiore Policlinico, Milan:
- Department of Pediatric Anesthesia and Intensive Care, Spedali Civili, Brescia
- Department of Neonatal and Paediatric Intensive Care, Azienda Ospedaliera Universitaria Integrata, Verona
- Department of Woman’s and Child’s Health, Pediatric ICU, University Hospital, Padova
- Department of Anesthesia and Intensive Care, Institute for Maternal and Child health, IRCCS Burlo Garofolo, Trieste
- Department of Pediatric Anesthesia and Intensive Care, Ospedale Sant’Orsola Malpighi, Bologna
- Department of Anesthesia and Intensive Care, Children’s Hospital Meyer, Firenze
- Department of Anesthesia and Intensive Care, Children’s Hospital Bambino Gesù, Rome DEA, ARCO, Palidoro
- Anesthesia and Intensive Care Department, Pediatric ICU, Policlinico Universitario A.Gemelli, Università Cattolica
del Sacro Cuore, Rome
- Department of Anesthesia and Intensive Care, Children’s Hospital Santobono-Pausillipon, Napoli
- Department of Anesthesia and Intensive Care, Children’s Hospital G Di Cristina, Palermo
- Department of Anesthesia and Intensive Care Ospedale Garibaldi – Nesima, Catania
- Department of Pediatrics Ospedale Policlinico –Universitario G Martino, Messina


```{r, child = "010-descriptives.Rmd"}
```

```{r, child = "020-origin.Rmd"}
```

```{r, child = "030-ccc.Rmd"}
```

```{r, child = "040-severity.Rmd"}
```

```{r, child = "050-los.Rmd"}
```



# References {-}
```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
